\documentclass[article]{jss}
\usepackage[utf8]{inputenc}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}

\author{
Tohru Yamaguchi\\Kao Corporation \And Second Author\\Affiliation
}
\title{A Capitalized Title: Something about a Package \pkg{foo}}

\Plainauthor{Tohru Yamaguchi, Second Author}
\Plaintitle{A Capitalized Title: Something about a Package foo}
\Shorttitle{\pkg{LKmodel}: A Package for household infectious mathmatical model}

\Abstract{
For a estimation of the infectiveness under the assumption of
mathematical model, either of the basic reproduction number which is an
estimate of the number of secondary infected persons from one infected
patient or the secondary infection risk (SIR) with exposure of one
infected patient in small-scale groups such as house and school is
frequently employed. Longini and Koopman proposed an infectious disease
mathematical model (L-K model) which estimating an infection risk from
distribution of the number of infected patients in the home within one
season. There are two parameters, B and Q, which should be estimated in
this model, 1-B can be interpreted medically as the infection
probability from a community, and 1-Q as the household secondary attack
rate which is an index of SIR. Although a previous paper described the
estimation method for these parameters in an epidemiological observation
study, the statistical test method for the clinical trial which compares
two intervention groups was not studied. In order to show the efficacy
of the medical agent under development, it is necessary to plan, carry
out and conduct data-analysis of the clinical trial however, the
calculation of the required number of subjects is impossible without the
appropriate test method. Then, the parameter estimation method was
extended, and the test method for the difference of Q between 2 groups
in this L-K model was newly developed. The developed tests were derived
from the framework of the statistical test method for the likelihood
based-model called a --likelihood ratio test--, --Wald test--, and
--score test--. The computational procedure was packed into the computer
program and the parameter was estimated from the data in the previous
paper. As a result, the calculation result described in the paper was
reproduced. Moreover, the number of subjects in a clinical trial was
estimated from Monte Carlo simulation using the developed test method,
and the reasonable results were obtained. It is thought that the
developed statistical test method has progressivity in respect of the
method which was not considered.
}

\Keywords{keywords, not capitalized, \proglang{Java}}
\Plainkeywords{keywords, not capitalized, Java}

%% publication information
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{}
%% \Acceptdate{2012-06-04}

\Address{
    Tohru Yamaguchi\\
  Kao Corporation\\
  2-1-3 Bunka Simida Tokyo, 131-8501 Japan\\
  E-mail: \email{yamaguchi.tohru@kao.com}\\
  URL: \url{http://rstudio.com}\\~\\
    }

% Pandoc header

\usepackage{amsmath}

\begin{document}

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

This template demonstrates some of the basic latex you'll need to know
to create a JSS article.

\hypertarget{code-formatting}{%
\subsection{Code formatting}\label{code-formatting}}

Don't use markdown, instead use the more precise latex commands:

\begin{itemize}
\item
  \proglang{Java}
\item
  \pkg{plyr}
\item
  \code{print("abc")}
\end{itemize}

\hypertarget{r-code}{%
\section{R code}\label{r-code}}

Can be inserted in regular R markdown blocks.

\begin{CodeChunk}

\begin{CodeInput}
R> x <- 1:10
R> x
\end{CodeInput}

\begin{CodeOutput}
 [1]  1  2  3  4  5  6  7  8  9 10
\end{CodeOutput}
\end{CodeChunk}



\end{document}

